Embodied Neuromorphic Benchmarks

### 2015-08-14 paper/paper.tex
Fixed typo
Added edits Chris and Travis

Notice that we can think of this system as a three-layer neural
network, where the input and output layers are linear.  The first layer is $q$, the input state, one value for each joint.  The ``hidden'' layer
is the neurons producing activities $A$, the activity of a large number of neurons.  The output layer again has
one value per joint, and is the extra added signal to apply to the motors, $Ad$.
Given that this is a canonical example of the use of neural networks, we
expect that the majority of neuromorphic hardware is flexible enough to implement
this model.  Importantly, it functions well with spiking neuron models as 
well as non-spiking ones.  For spiking neurons, we consider $A$ to be the
instantaneous measure of the output of a neuron (i.e. whether or not it is currently outputing a spike),
filtered through a low-pass filter.  Further discussion of this sort of learning
rule and comparison to biological spiking neurons is given by [ref?].

@@

In addition, we add a external perturbing forces.  In a real system,
this could be the effects of gravity given the current configuration of the
motors, or of other unexpected influences.  
Rather than chosing one particular fixed external force for our benchmark,
we \emph{randomly generate} this force each time the benchmark is run.  This
ensures that the benchmark covers a wide range of possible external forces
and motor configurations, rather than just one particular situation.

@@

With the minimal simulation approach, we perform a benchmark by taking a
particular piece of hardware, using it to control a minimal simulation, and
measure some aspect of that simulation.  We perform this test multiple times,
and each time we choose a different set of random parameters for the
simulation.  A particular benchmark, then, will also provide particular
distributions for these parameters.

@@

We can also use this sort of benchmark to examine the effects of various
parameters in the model.  For example, in Figure \ref{fig:analysis_delay_cpu}
we show what happens as the delays $\t_q$ and $\t_u$ are increased.
Importantly, the range on these parameters is larger than before ($U(0, 0.04)$
rather than $U(0, 0.01)$).  This shows that if the delay is short (less than 0.02), the controller performs well, and if it is very large (greater than 0.03),
the controller performs poorly.  However, for delays between 0.02 and 0.03,
the controller will sometimes perform well and sometimes perform poorly.  The
difference is due to the other random parameters in the system.  Interestingly,
running this same benchmark on SpiNNaker in Figure \ref{fig:analysis_delay_spinn} shows that SpiNNaker actually performs better on this
task.  Further analysis is needed to determine exactly why this is.

>>>>

Notice that we can think of this system as a three-layer neural
network, where the input and output layers are linear.  The first layer is $q$, the input state, one value for each joint.  The ``hidden'' layer
is the neurons producing activities $A$, the activity of a large number of neurons.  The output layer again has
one value per joint, and is the extra added signal to apply to the motors, $Ad$.
Given that this is a canonical example of the use of neural networks, we
expect that the majority of neuromorphic hardware is flexible enough to implement
this model.  Importantly, it functions well with spiking neuron models as 
well as non-spiking ones.  For spiking neurons, we consider $A$ to be the
instantaneous measure of the output of a neuron (i.e. whether or not it is currently outputing a spike),
filtered through a low-pass filter.  Further discussion of this sort of learning
rule and comparison to biological spiking neurons can be found in (\citealt{bekolay2013}).

@@

In addition, we add an external perturbing force.  In a real system,
this could be the effects of gravity given the current configuration of the
motors, or of other unexpected influences.  
Rather than chosing one particular fixed external force for our benchmark,
we \emph{randomly generate} this force each time the benchmark is run.  This
ensures that the benchmark covers a wide range of possible external forces
and motor configurations, rather than just one particular situation.

@@

With the minimal simulation approach, we perform a benchmark by taking a
particular piece of hardware and using it to control a minimal simulation while
measuring some aspect of that simulation.  We perform this test multiple times,
and each time we choose a different set of random parameters for the
simulation.  A particular benchmark, then, will also provide particular
distributions for these parameters.

@@

We can also use this sort of benchmark to examine the effects of various
parameters in the model.  For example, in Figure \ref{fig:analysis_delay_cpu}
we show what happens as the delays $t_q$ and $t_u$ are increased.
Importantly, the range on these parameters is larger than before ($U(0, 0.04)$
rather than $U(0, 0.01)$).  This shows that if the delay is short (less than 0.02), the controller performs well, and if it is very large (greater than 0.03),
the controller performs poorly.  However, for delays between 0.02 and 0.03,
the controller will sometimes perform well and sometimes perform poorly.  The
difference is due to the other random parameters in the system.  Interestingly,
running this same benchmark on SpiNNaker in Figure \ref{fig:analysis_delay_spinn} shows that SpiNNaker actually performs better on this
task.  Further analysis is needed to determine exactly why this is.
